pema application

### 2022-12-05 paper/manuscript.Rmd
acknowledge brms
corrected defaults origin

For estimation, `brma()` depends on Stan, a probabilistic programming language that uses Hamiltonian Monte Carlo to sample from the posterior distribution [@rstan].
Stan is written in C++, and thus computationally efficient, but custom models must be compiled prior to estimation.
Installing a toolchain to compile models requires some technical sophistication, which potentially restricts the user base.
Moreover, model compilation adds unnecessary computational overhead for standard applications.
To overcome these limitations, the `pema` package includes pre-compiled stock models with opinionated default options.
At the time of writing, these include random effects and three-level meta-regression with and without an intercept.
R-users can refer to the package documentation to see what options are available at the time of reading by running `?pema::brma`.
Researchers who wish to construct a model that is currently out of scope of `brma()` are referred to `rstan` instead [@rstan].
As a starting point, the `rstan` source code for the stock models included with `pema` can be accessed by running `pema:::stanmodels`.
We welcome user contributions of additional models.

@@

We performed a simulation study to validate the BRMA algorithm.
As a benchmark for comparison, we used random effects meta-regression with restricted maximum likelihood estimation [RMA, @viechtbauerConductingMetaanalysesMetafor2010],
which is the current state-of-the-art in the field.
We evaluated the algorithms' predictive performance in new data, 
ability to perform variable selection,
and ability to recover population parameters.
Our research questions are whether BRMA offers a performance advantage over RMA in terms of any of these indicators,
and which prior (LASSO versus regularized horseshoe) is to be preferred.
<span id = "defaultvalues">For both Bayesian priors, we used default values proposed in prior literature, see Table \@ref(tab:tabprior).
Default values for the LASSO prior were based on @vanErpOberskiMulder2019,
and default values for the regularized horseshoe prior were based on @PiironenVehtari2017a.</span>
All analysis code is available in a version-controlled repository at <https://github.com/cjvanlissa/pema>.

>>>>

For estimation, `brma()` depends on Stan, a probabilistic programming language that uses Hamiltonian Monte Carlo to sample from the posterior distribution [@rstan].
Stan is written in C++, and thus computationally efficient, but custom models must be compiled prior to estimation.
Installing a toolchain to compile models requires some technical sophistication, which potentially restricts the user base.
Moreover, model compilation adds unnecessary computational overhead for standard applications.
To overcome these limitations, the `pema` package includes pre-compiled stock models with opinionated default options. These models have been created using the `brms` package [@R-brms_a].
At the time of writing, these include random effects and three-level meta-regression with and without an intercept.
R-users can refer to the package documentation to see what options are available at the time of reading by running `?pema::brma`.
Researchers who wish to construct a model that is currently out of scope of `brma()` are referred to `rstan` instead [@rstan].
As a starting point, the `rstan` source code for the stock models included with `pema` can be accessed by running `pema:::stanmodels`.
We welcome user contributions of additional models.

@@

We performed a simulation study to validate the BRMA algorithm.
As a benchmark for comparison, we used random effects meta-regression with restricted maximum likelihood estimation [RMA, @viechtbauerConductingMetaanalysesMetafor2010],
which is the current state-of-the-art in the field.
We evaluated the algorithms' predictive performance in new data, 
ability to perform variable selection,
and ability to recover population parameters.
Our research questions are whether BRMA offers a performance advantage over RMA in terms of any of these indicators,
and which prior (LASSO versus regularized horseshoe) is to be preferred.
<span id = "defaultvalues">For both Bayesian priors, we used default values proposed in prior literature, see Table \@ref(tab:tabprior).
Default values for the LASSO prior were based on the defaults used in @R-brms_a,
and default values for the regularized horseshoe prior were based on @PiironenVehtari2017a.</span>
All analysis code is available in a version-controlled repository at <https://github.com/cjvanlissa/pema>.
